\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=2.5cm]{geometry}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{float}
\usepackage{enumitem}
\usepackage[dvipsnames]{xcolor}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{tcolorbox}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}

\usetikzlibrary{arrows.meta,positioning,calc,fit,backgrounds,shapes.geometric}

\tcbuselibrary{listings,skins,breakable}

\definecolor{astropurple}{HTML}{7C3AED}
\definecolor{astrodark}{HTML}{1E1B2E}
\definecolor{astroaccent}{HTML}{A78BFA}
\definecolor{codebg}{HTML}{F8F5FF}
\definecolor{codeframe}{HTML}{DDD6FE}
\definecolor{rustcolor}{HTML}{CE422B}
\definecolor{tscolor}{HTML}{3178C6}
\definecolor{wgslcolor}{HTML}{4CAF50}
\definecolor{sectioncolor}{HTML}{4C1D95}
\definecolor{linkcolor}{HTML}{6D28D9}
\definecolor{notebg}{HTML}{FEF3C7}
\definecolor{noteframe}{HTML}{F59E0B}

\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    urlcolor=linkcolor,
    citecolor=linkcolor,
    pdftitle={AstroBurst Technical Document},
    pdfauthor={Samuel Krieger Bonini},
    pdfsubject={High-Performance Astronomical Image Processor},
}

\lstdefinestyle{rustcode}{
    language=C,
    backgroundcolor=\color{codebg},
    frame=single,
    rulecolor=\color{codeframe},
    basicstyle=\ttfamily\small,
    keywordstyle=\color{rustcolor}\bfseries,
    commentstyle=\color{gray},
    stringstyle=\color{ForestGreen},
    numbers=left,
    numberstyle=\tiny\color{gray},
    numbersep=8pt,
    breaklines=true,
    showstringspaces=false,
    tabsize=4,
    morekeywords={fn,let,mut,pub,struct,impl,use,mod,async,await,match,enum,trait,where,Self,self,crate,super,dyn,Box,Vec,Option,Result,Ok,Err,Some,None},
    literate={->}{{$\rightarrow$}}1 {=>}{{$\Rightarrow$}}1,
}

\lstdefinestyle{tscode}{
    language=Java,
    backgroundcolor=\color{codebg},
    frame=single,
    rulecolor=\color{codeframe},
    basicstyle=\ttfamily\small,
    keywordstyle=\color{tscolor}\bfseries,
    commentstyle=\color{gray},
    stringstyle=\color{ForestGreen},
    numbers=left,
    numberstyle=\tiny\color{gray},
    numbersep=8pt,
    breaklines=true,
    showstringspaces=false,
    tabsize=2,
    morekeywords={const,let,async,await,interface,type,export,import,from,as,extends},
}

\lstdefinestyle{bashcode}{
    language=bash,
    backgroundcolor=\color{codebg},
    frame=single,
    rulecolor=\color{codeframe},
    basicstyle=\ttfamily\small,
    keywordstyle=\color{astropurple}\bfseries,
    numbers=none,
    breaklines=true,
    showstringspaces=false,
}

\newtcolorbox{notebox}[1][]{
    colback=notebg,
    colframe=noteframe,
    fonttitle=\bfseries,
    title={#1},
    arc=2pt,
    boxrule=0.5pt,
    left=6pt,
    right=6pt,
    top=4pt,
    bottom=4pt,
}

\newtcolorbox{infobox}[1][]{
    colback=codebg,
    colframe=astropurple,
    fonttitle=\bfseries\color{white},
    colbacktitle=astropurple,
    title={#1},
    arc=2pt,
    boxrule=0.5pt,
    left=6pt,
    right=6pt,
    top=4pt,
    bottom=4pt,
}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\textcolor{gray}{AstroBurst --- Technical Document v0.3.0}}
\fancyhead[R]{\small\textcolor{gray}{\thepage}}
\fancyfoot[C]{\small\textcolor{gray}{GPL-3.0 License \textbullet\ \the\year}}
\renewcommand{\headrulewidth}{0.4pt}
\renewcommand{\footrulewidth}{0pt}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

\newcommand{\code}[1]{\texttt{\small #1}}
\newcommand{\crate}[1]{\texttt{#1}}
\newcommand{\cmd}[1]{\texttt{\bfseries #1}}
\newcommand{\mat}[1]{\mathbf{#1}}

\title{
    \vspace{-1cm}
    {\Huge\bfseries\textcolor{astropurple}{AstroBurst}}\\[0.3cm]
    {\Large High-Performance Astronomical Image Processor}\\[0.2cm]
    {\large Technical Document --- Release v0.3.0}
}
\author{Samuel Krieger Bonini}
\date{March 2026}

\begin{document}

    \maketitle
    \thispagestyle{empty}

    \vspace{0.5cm}

    \begin{center}
        \begin{tabular}{ll}
            \toprule
            \textbf{Field} & \textbf{Value} \\
            \midrule
            Document Version & 0.3.0 \\
            Release & v0.3.0 \\
            Date & March 2026 \\
            Author & Samuel Krieger Bonini \\
            Stack & Rust 1.75+ $\cdot$ Tauri v2 $\cdot$ React $\cdot$ TypeScript \\
            Platforms & Windows $\cdot$ macOS $\cdot$ Linux \\
            License & GPL-3.0-or-later \\
            Repository & \url{https://github.com/samuelkriegerbonini-dev/AstroBurst} \\
            \bottomrule
        \end{tabular}
    \end{center}

    \vspace{0.5cm}
    \tableofcontents
    \newpage

%% ============================================================================
    \section{Executive Summary}
%% ============================================================================

    AstroBurst is a cross-platform desktop application for processing, analyzing, and visualizing astronomical FITS and ASDF images. It is the first astronomical image processor built on the \textbf{Rust/Tauri/WebGPU} stack, combining native-level performance with a modern, accessible user interface.

    The application targets two user segments:
    \begin{itemize}[nosep]
    \item Professional astronomers working with observatory data (JWST, Hubble, Roman Space Telescope, ground-based IFU instruments)
    \item Advanced astrophotographers processing deep-sky narrowband and broadband imaging data
    \end{itemize}

    Version 0.3.0 delivers a complete processing pipeline from raw FITS/ASDF ingestion through deconvolution, noise reduction, color composition, and export, with \textbf{41 backend commands} exposed through a typed TypeScript API layer. Of these, 20 commands are actively wired to the frontend UI, while 21 additional commands are backend-ready and awaiting UI panel integration.

    \subsection{What's New in v0.3.0}
    \begin{itemize}[nosep]
    \item \textbf{Richardson-Lucy deconvolution} --- FFT-based iterative deconvolution with Gaussian PSF, regularization, and deringing
    \item \textbf{Background extraction} --- Polynomial surface modeling with sigma-clipped grid sampling (subtract or divide modes)
    \item \textbf{Wavelet denoising} --- Multi-scale wavelet decomposition with per-scale sigma thresholds (up to 8 scales)
    \item \textbf{ASDF format support} --- First Rust implementation of the Advanced Scientific Data Format reader with zlib/bzip2/lz4 decompression, Roman Space Telescope data model traversal, and gWCS extraction
    \item \textbf{Redesigned tab UI} --- Bottom tabs (Info, Analysis, Headers, Export) + side panels (Processing, Compose) with resizable drag handles
    \item \textbf{Split preview contexts} --- 6 independent React contexts for minimal re-renders
    \item \textbf{Lazy-loaded panels} --- React.lazy + Suspense for fast initial load
    \end{itemize}

%% ============================================================================
    \section{System Architecture}
%% ============================================================================

    AstroBurst follows a strict backend/frontend separation, with all computation offloaded to Rust and all rendering handled by the browser engine embedded in Tauri.

    \begin{figure}[H]
        \centering
        \begin{tikzpicture}[
            layer/.style={draw, rounded corners=3pt, minimum width=14cm, minimum height=1.2cm, font=\small},
            sublayer/.style={draw, rounded corners=2pt, minimum height=0.8cm, font=\footnotesize, fill=white},
            arrow/.style={-{Stealth[length=3mm]}, thick, color=astropurple},
            label/.style={font=\footnotesize\bfseries, color=astropurple}
        ]

\node[layer, fill=tscolor!10, draw=tscolor] (frontend) at (0, 4.5) {};
\node[label] at (-5.5, 4.9) {Frontend};
\node[sublayer, fill=tscolor!5] at (-4.2, 4.5) {React};
\node[sublayer, fill=tscolor!5] at (-2, 4.5) {TypeScript};
\node[sublayer, fill=tscolor!5] at (0.3, 4.5) {Tailwind v4};
\node[sublayer, fill=tscolor!5] at (2.7, 4.5) {WebGPU};
\node[sublayer, fill=tscolor!5] at (4.8, 4.5) {Canvas 2D};

\node[layer, fill=astropurple!10, draw=astropurple] (ipc) at (0, 3) {};
\node[label] at (-5.5, 3.4) {IPC Bridge};
\node[sublayer, fill=astropurple!5] at (-3, 3) {JSON Commands};
\node[sublayer, fill=astropurple!5] at (0.5, 3) {Binary IPC};
\node[sublayer, fill=astropurple!5] at (3.5, 3) {Asset Protocol};

\node[layer, fill=rustcolor!10, draw=rustcolor, minimum height=3.5cm] (backend) at (0, 0.5) {};
\node[label] at (-5.5, 2.0) {Backend};

\node[sublayer, fill=rustcolor!5, minimum width=3.8cm] (cmds) at (-4.2, 1.5) {\texttt{cmd/ + core/}};
\node[sublayer, fill=rustcolor!5, minimum width=3.8cm] (domain) at (0, 1.5) {\texttt{domain/ + infra/}};
\node[sublayer, fill=rustcolor!5, minimum width=3.8cm] (utils) at (4.2, 1.5) {\texttt{types/ + math/}};

\node[font=\scriptsize, text=gray] at (-4.2, 0.9) {image, metadata, analysis};
\node[font=\scriptsize, text=gray] at (-4.2, 0.5) {cube, astrometry};
\node[font=\scriptsize, text=gray] at (-4.2, 0.1) {stacking, compose};

\node[font=\scriptsize, text=gray] at (0, 0.9) {FITS mmap, ASDF reader};
\node[font=\scriptsize, text=gray] at (0, 0.5) {cache, IPC, render};
\node[font=\scriptsize, text=gray] at (0, 0.1) {config, progress};

\node[font=\scriptsize, text=gray] at (4.2, 0.9) {STF, drizzle, FFT};
\node[font=\scriptsize, text=gray] at (4.2, 0.5) {deconv, wavelet};
\node[font=\scriptsize, text=gray] at (4.2, 0.1) {WCS, SCNR};

\draw[arrow] (frontend) -- (ipc);
\draw[arrow] (ipc) -- (backend);

        \end{tikzpicture}
        \caption{AstroBurst three-layer architecture}
        \label{fig:architecture}
    \end{figure}

    \subsection{Backend (Rust)}

    The Rust backend is organized into six layers:

    \begin{description}[style=nextline, leftmargin=2cm]
    \item[\texttt{cmd/}] Tauri command handlers organized by domain (41 registered commands). Each module receives deserialized JSON arguments, delegates to core/domain logic, and returns JSON or binary responses.
    \item[\texttt{core/}] Pure computational modules: analysis (histogram, FFT, stars), astrometry (plate solve, WCS), compose (RGB, SCNR, white balance), cube (spectrum, frames), imaging (STF, deconvolution, wavelet, background), metadata (header discovery, filter detection), stacking (sigma-clip, drizzle).
    \item[\texttt{domain/}] Orchestration layer coordinating core modules for complex multi-step operations (pipeline, batch).
    \item[\texttt{infra/}] Infrastructure: Arc-based zero-copy cache, config management, FITS I/O (mmap parser, MEF scanner, FITS writer), ASDF reader (YAML tree parser, binary block extractor, zlib/bzip2/lz4 decompressor, Roman data model converter, gWCS bridge), binary IPC encoding, progress tracking, PNG rendering.
    \item[\texttt{types/}] Shared type definitions: image stats, STF params, stacking/drizzle/RL configs, compose types, SCNR, error types, FITS header abstraction, constants.
    \item[\texttt{math/}] Mathematical primitives shared across core modules.
    \end{description}

    All heavy computation is offloaded via \code{tokio::task::spawn\_blocking}, preventing UI freezes. Batch operations use Rayon for data-parallel execution across all available CPU cores.

    \subsection{Frontend (React + TypeScript)}

    The frontend is a single-page React application with a tab-based layout:

    \begin{description}[style=nextline, leftmargin=2cm]
    \item[\texttt{App.tsx}] Root component managing view state (empty/processing/complete), file dialog integration, drag-and-drop, resizable sidebar, and folder scanning.
    \item[\texttt{useFileQueue}] Central state machine (\code{useReducer}) tracking file status, concurrent processing queue (3 workers), resolution group detection, and auto-resampling.
    \item[\texttt{useBackend}] Typed Tauri IPC wrapper exposing all 41 commands with automatic URL resolution for \code{asset://} protocol paths and downsampled binary pixel transfer.
    \item[Tab System] Bottom tabs: Info (stats/header summary), Analysis (histogram, FFT, stars, spectroscopy), Headers (full header explorer), Export (FITS/PNG). Side tabs: Processing (background extraction, wavelet denoise, deconvolution), Compose (RGB, drizzle, drizzle RGB).
    \item[Preview Contexts] 6 split React contexts (FileCtx, HistCtx, CubeCtx, RgbCtx, RenderCtx, RawPixelsCtx) providing scoped state to avoid cascading re-renders.
    \item[Lazy Loading] All panel components loaded via \code{React.lazy} + \code{Suspense} with spinner fallbacks.
    \end{description}

    \subsection{IPC Strategy}

    Two IPC channels are used:

    \begin{infobox}[Binary IPC Protocol]
        The \cmd{get\_raw\_pixels\_preview} and \cmd{get\_raw\_pixels\_binary} commands encode a \textbf{16-byte header} followed by raw pixel data:
        \begin{center}
            \begin{tabular}{cccl}
                \toprule
                \textbf{Offset} & \textbf{Type} & \textbf{Size} & \textbf{Description} \\
                \midrule
                0 & \code{u32} & 4B & Image width \\
                4 & \code{u32} & 4B & Image height \\
                8 & \code{f32} & 4B & Data minimum \\
                12 & \code{f32} & 4B & Data maximum \\
                16 & \code{f32[]} & $W \times H \times 4$B & Raw pixel values \\
                \bottomrule
            \end{tabular}
        \end{center}
        The frontend receives an \code{ArrayBuffer} directly with zero JSON/base64 overhead.
    \end{infobox}

%% ============================================================================
    \section{Mathematical Foundations}
    \label{sec:math}
%% ============================================================================

    \subsection{Screen Transfer Function (STF)}
    \label{sec:stf}

    The STF implements the PixInsight-style \textbf{Midtone Transfer Function} (MTF). Given a normalized pixel value $x \in [0, 1]$ and midtone parameter $m \in (0, 1)$:

    \begin{equation}
        \boxed{
            \text{MTF}(x, m) = \frac{(m - 1) \cdot x}{(2m - 1) \cdot x - m}
        }
        \label{eq:mtf}
    \end{equation}

    \textbf{Properties:}
    \begin{itemize}[nosep]
    \item $\text{MTF}(0, m) = 0$ and $\text{MTF}(1, m) = 1$ for all $m$
    \item $\text{MTF}(m, m) = 0.5$ --- the midtone maps to 50\% brightness
    \item $m < 0.5$ brightens the image; $m > 0.5$ darkens it
    \end{itemize}

    The \textbf{auto-stretch} algorithm computes the stretch parameters from image statistics. Given the pixel distribution, let $\tilde{x}$ be the median and $\text{MAD}$ the Median Absolute Deviation:

    \begin{align}
        \text{MAD} &= \text{median}\left(|x_i - \tilde{x}|\right) \label{eq:mad} \\[6pt]
        \text{shadow} &= \max\left(0,\; \tilde{x} - k \cdot \text{MAD}\right) \label{eq:shadow} \\[6pt]
        \text{midtone} &= \text{MTF}^{-1}\left(t_{\text{bg}},\; \frac{\tilde{x} - \text{shadow}}{1 - \text{shadow}}\right) \label{eq:midtone} \\[6pt]
        \text{highlight} &= 1.0 \label{eq:highlight}
    \end{align}

    where $k = 2.8$ (calibrated for deep-sky data) and $t_{\text{bg}} = 0.25$ is the target background level. The clipping function is then:

    \begin{equation}
        \text{STF}(x) = \text{MTF}\!\left(\text{clip}\!\left(\frac{x - s}{h - s},\; 0,\; 1\right),\; m\right)
        \label{eq:stf}
    \end{equation}

    where $s$, $m$, $h$ are the shadow, midtone, and highlight parameters.

    \subsection{Asinh Stretch}

    The \textbf{arcsinh transfer function} provides astronomically-correct normalization that preserves flux ratios between stars of different magnitudes:

    \begin{equation}
        \boxed{
            f(x) = \frac{\operatorname{asinh}(\alpha \cdot x)}{\operatorname{asinh}(\alpha)}
        }
        \label{eq:asinh}
    \end{equation}

    where $\alpha$ controls the stretch aggressiveness. This function maps $[0, 1] \to [0, 1]$ and is approximately linear for small $x$ (preserving faint detail) while compressing bright values logarithmically.

    \subsection{Sigma-Clipped Stacking}
    \label{sec:sigma_stack}

    Frames are registered via \textbf{cross-correlation} (phase correlation in frequency domain), then stacked with iterative sigma clipping.

    \begin{algorithm}[H]
\SetAlgoLined
\SetKwInOut{Input}{Input}
\SetKwInOut{Output}{Output}
\Input{Aligned frames $\{F_1, F_2, \ldots, F_N\}$, thresholds $\sigma_{\text{low}}, \sigma_{\text{high}}$, max iterations $K$}
\Output{Stacked image $S$}
\ForEach{pixel position $(i, j)$}{
    $V \leftarrow \{F_1(i,j), F_2(i,j), \ldots, F_N(i,j)\}$\;
    \For{$k = 1$ \KwTo $K$}{
        $\mu \leftarrow \text{mean}(V)$\;
        $\sigma \leftarrow \text{std}(V)$\;
        $V' \leftarrow \{v \in V : \mu - \sigma_{\text{low}} \cdot \sigma \leq v \leq \mu + \sigma_{\text{high}} \cdot \sigma\}$\;
        \If{$|V'| = |V|$ \textbf{or} $|V'| < 3$}{
            \textbf{break}\;
        }
        $V \leftarrow V'$\;
    }
    $S(i,j) \leftarrow \text{mean}(V)$\;
}
\caption{Iterative Sigma-Clipped Stacking}
\label{alg:sigma_clip}
    \end{algorithm}

    Default parameters: $\sigma_{\text{low}} = \sigma_{\text{high}} = 3.0$, $K = 5$.

    \subsection{Drizzle Integration}
    \label{sec:drizzle}

    Drizzle (Variable-Pixel Linear Reconstruction) maps input pixels onto a higher-resolution output grid. For an input pixel $p$ at fractional position $(x_f, y_f)$ on the output grid:

    \begin{equation}
        O(i, j) = \frac{\sum_p w_p \cdot K(i - x_f^p,\; j - y_f^p) \cdot I_p}{\sum_p w_p \cdot K(i - x_f^p,\; j - y_f^p)}
        \label{eq:drizzle}
    \end{equation}

    where $K$ is the drizzle kernel and $w_p$ is the pixel weight. Three kernel options are implemented:

    \begin{align}
        K_{\text{square}}(\Delta x, \Delta y) &=
        \begin{cases}
            1 & \text{if } |\Delta x| \leq \frac{d}{2} \text{ and } |\Delta y| \leq \frac{d}{2} \\
            0 & \text{otherwise}
        \end{cases}
        \label{eq:kernel_square} \\[8pt]
        K_{\text{gaussian}}(\Delta x, \Delta y) &= \exp\!\left(-\frac{\Delta x^2 + \Delta y^2}{2\sigma_K^2}\right)
        \label{eq:kernel_gaussian} \\[8pt]
        K_{\text{lanczos3}}(\Delta x, \Delta y) &= L_3(\Delta x) \cdot L_3(\Delta y)
        \label{eq:kernel_lanczos}
    \end{align}

    where $d = \text{pixfrac} / \text{scale}$ and the Lanczos-3 kernel is:

    \begin{equation}
        L_3(x) =
        \begin{cases}
            \operatorname{sinc}(x) \cdot \operatorname{sinc}(x/3) & \text{if } |x| < 3 \\
            0 & \text{otherwise}
        \end{cases}
        \label{eq:lanczos}
    \end{equation}

    The weight map $W(i,j) = \sum_p w_p \cdot K(\cdot)$ tracks per-pixel coverage for noise estimation.

    \subsection{Cross-Correlation Alignment}
    \label{sec:alignment}

    Frame registration uses \textbf{phase correlation} in the frequency domain. Given reference frame $R$ and target frame $T$:

    \begin{equation}
        \text{shift} = \arg\max_{(\Delta x, \Delta y)} \mathcal{F}^{-1}\!\left\{\frac{\hat{R} \cdot \hat{T}^*}{|\hat{R} \cdot \hat{T}^*|}\right\}
        \label{eq:phase_corr}
    \end{equation}

    where $\hat{R} = \mathcal{F}\{R\}$ denotes the 2D DFT. The normalized cross-power spectrum produces a sharp peak at the integer translation offset.

    \subsection{World Coordinate System (WCS)}
    \label{sec:wcs}

    WCS transforms use the \textbf{CD matrix formulation} with TAN (gnomonic) projection. Given reference pixel $(\text{CRPIX}_1, \text{CRPIX}_2)$ and reference coordinate $(\alpha_0, \delta_0) = (\text{CRVAL}_1, \text{CRVAL}_2)$:

    \subsubsection{Forward Transform (Pixel $\to$ World)}

    \begin{equation}
        \begin{pmatrix} u \\ v \end{pmatrix} =
        \begin{pmatrix} \text{CD}_{1,1} & \text{CD}_{1,2} \\ \text{CD}_{2,1} & \text{CD}_{2,2} \end{pmatrix}
        \begin{pmatrix} x - \text{CRPIX}_1 \\ y - \text{CRPIX}_2 \end{pmatrix}
        \label{eq:wcs_forward}
    \end{equation}

    where $(u, v)$ are intermediate world coordinates in degrees. The TAN deprojection yields:

    \begin{align}
        \alpha &= \alpha_0 + \arctan\!\left(\frac{u}{cos(\delta_0) - v \cdot \sin(\delta_0)}\right) \label{eq:wcs_ra} \\[4pt]
        \delta &= \arctan\!\left(\frac{v \cdot \cos(\delta_0) + \sin(\delta_0)}{\sqrt{u^2 + (\cos(\delta_0) - v \cdot \sin(\delta_0))^2}}\right) \label{eq:wcs_dec}
    \end{align}

    \subsubsection{Pixel Scale}

    \begin{equation}
        \text{scale} = \sqrt{|\det(\mat{CD})|} \times 3600 \quad [\text{arcsec/pixel}]
        \label{eq:pixel_scale}
    \end{equation}

    \subsubsection{Inverse Transform (World $\to$ Pixel)}

    \begin{equation}
        \begin{pmatrix} x \\ y \end{pmatrix} =
        \mat{CD}^{-1}
        \begin{pmatrix} u \\ v \end{pmatrix}
        +
        \begin{pmatrix} \text{CRPIX}_1 \\ \text{CRPIX}_2 \end{pmatrix}
        \label{eq:wcs_inverse}
    \end{equation}

    \subsection{FFT Power Spectrum}
    \label{sec:fft}

    The 2D power spectrum for noise characterization is computed as:

    \begin{equation}
        P(u, v) = \log_{10}\!\left(1 + |\hat{I}(u, v)|^2\right)
        \label{eq:power_spectrum}
    \end{equation}

    where $\hat{I} = \mathcal{F}\{I\}$ is the 2D DFT of the image. The DC component at $(0, 0)$ is shifted to the center for visualization. The spectrum is normalized to $[0, 1]$ after computation.

    \subsection{Star Detection (PSF Centroid)}
    \label{sec:star_detection}

    Background is estimated via iterative sigma-clipped median. Pixels above $\tilde{b} + \sigma_{\text{thresh}} \cdot \sigma_b$ are identified as candidates. For each connected component $C$:

    \begin{align}
        \bar{x}_C &= \frac{\sum_{(i,j) \in C} i \cdot (I_{ij} - b)}{\sum_{(i,j) \in C} (I_{ij} - b)}
        & \bar{y}_C &= \frac{\sum_{(i,j) \in C} j \cdot (I_{ij} - b)}{\sum_{(i,j) \in C} (I_{ij} - b)} \label{eq:centroid} \\[6pt]
        F_C &= \sum_{(i,j) \in C} (I_{ij} - b)
        & \text{SNR}_C &= \frac{F_C}{\sqrt{|C| \cdot \sigma_b^2}} \label{eq:flux_snr}
    \end{align}

    FWHM is estimated from the second intensity moments:

    \begin{equation}
        \text{FWHM} = 2\sqrt{2\ln 2} \cdot \sqrt{\frac{\sigma_x^2 + \sigma_y^2}{2}}
        \label{eq:fwhm}
    \end{equation}

    where $\sigma_x^2, \sigma_y^2$ are the variance of pixel positions weighted by intensity.

    \subsection{SCNR (Subtractive Chromatic Noise Reduction)}
    \label{sec:scnr}

    SCNR removes green channel excess in narrowband compositions. Two methods are implemented:

    \begin{align}
        G'_{\text{average}} &= \min\!\left(G,\; \frac{R + B}{2}\right) \label{eq:scnr_avg} \\[4pt]
        G'_{\text{max}} &= \min\!\left(G,\; \max(R, B)\right) \label{eq:scnr_max}
    \end{align}

    \subsection{Calibration Pipeline}
    \label{sec:calibration}

    The standard CCD calibration formula applies bias, dark current, and flat field corrections:

    \begin{equation}
        \boxed{
            I_{\text{calibrated}} = \frac{I_{\text{raw}} - M_{\text{bias}} - r \cdot M_{\text{dark}}}{M_{\text{flat}} / \overline{M_{\text{flat}}}}
        }
        \label{eq:calibration}
    \end{equation}

    where $M_{\text{bias}}$, $M_{\text{dark}}$, $M_{\text{flat}}$ are master calibration frames (median-combined), $r$ is the exposure ratio (science/dark), and $\overline{M_{\text{flat}}}$ is the mean value of the flat field.

    \subsection{White Balance}
    \label{sec:white_balance}

    Auto white balance normalizes each channel by its median value:

    \begin{equation}
        C'_k = \frac{C_k}{\tilde{C}_k} \cdot \min(\tilde{C}_R, \tilde{C}_G, \tilde{C}_B), \quad k \in \{R, G, B\}
        \label{eq:white_balance}
    \end{equation}

    \subsection{Richardson-Lucy Deconvolution (v0.3.0)}
    \label{sec:rl_deconv}

    The Richardson-Lucy algorithm iteratively estimates the true image $f$ given observed image $g$ and point spread function $h$:

    \begin{equation}
        f^{(k+1)} = f^{(k)} \cdot \left( \frac{g}{f^{(k)} * h} * \hat{h} \right)
        \label{eq:rl}
    \end{equation}

    where $*$ denotes convolution, $\hat{h}$ is the PSF flipped about both axes, and $f^{(0)} = g$. Convolutions are computed in the frequency domain via FFT for efficiency:

    \begin{equation}
        f^{(k)} * h = \mathcal{F}^{-1}\left\{\hat{F}^{(k)} \cdot \hat{H}\right\}
    \end{equation}

    where $\hat{F}^{(k)} = \mathcal{F}\{f^{(k)}\}$ and $\hat{H} = \mathcal{F}\{h\}$. The PSF is modeled as a 2D Gaussian:

    \begin{equation}
        h(x, y) = \frac{1}{2\pi\sigma^2} \exp\left(-\frac{x^2 + y^2}{2\sigma^2}\right)
    \end{equation}

    with configurable $\sigma$ (default 2.0) and kernel size (default $15 \times 15$). Tikhonov regularization is applied:

    \begin{equation}
        f^{(k+1)}_{\text{reg}} = \frac{f^{(k+1)}}{1 + \lambda \nabla^2 f^{(k+1)}}
    \end{equation}

    where $\lambda$ is the regularization parameter (default 0.001). Optional deringing suppresses ringing artifacts near bright edges by clamping values that exceed a threshold above the local median.

    \subsection{Background Extraction (v0.3.0)}
    \label{sec:background}

    Background is modeled as a polynomial surface fitted to sigma-clipped grid samples:

    \begin{enumerate}[nosep]
    \item Divide the image into an $N \times N$ grid (default $N = 8$)
    \item For each cell, compute the sigma-clipped median (default $\sigma = 2.5$, 3 iterations) to reject stars and nebulosity
    \item Fit a 2D polynomial of degree $d$ (default $d = 3$) to the grid medians using least squares:
    \end{enumerate}

    \begin{equation}
        B(x, y) = \sum_{i=0}^{d} \sum_{j=0}^{d-i} a_{ij} \, x^i \, y^j
        \label{eq:background}
    \end{equation}

    Two correction modes are supported:

    \begin{equation}
        I_{\text{corrected}} = \begin{cases}
                                   I - B & \text{(subtract mode)} \\
                                   I / B & \text{(divide mode)}
        \end{cases}
    \end{equation}

    \subsection{Wavelet Denoising (v0.3.0)}
    \label{sec:wavelet}

    Multi-scale wavelet denoising uses the \`{a} trous (``with holes'') algorithm. The image is decomposed into $N$ wavelet scales $W_k$ and a residual $c_N$:

    \begin{equation}
        I = \sum_{k=1}^{N} W_k + c_N
    \end{equation}

    where each wavelet scale $W_k = c_{k-1} - c_k$ captures structures at spatial frequency $2^k$ pixels. The smoothed approximation $c_k$ is obtained by convolving $c_{k-1}$ with a B3 spline kernel dilated by factor $2^{k-1}$.

    Denoising applies a hard threshold to each scale:

    \begin{equation}
        W'_k(x, y) = \begin{cases}
                         W_k(x, y) & \text{if } |W_k(x, y)| > \sigma_k \cdot t_k \\
                         0 & \text{otherwise}
        \end{cases}
    \end{equation}

    where $\sigma_k$ is the noise estimate at scale $k$ (from the MAD of the wavelet coefficients) and $t_k$ is the per-scale threshold (default: 3.0, 2.5, 2.0, 1.5, 1.0 for scales 1--5). The denoised image is reconstructed as:

    \begin{equation}
        I' = \sum_{k=1}^{N} W'_k + c_N
    \end{equation}

    Up to 8 decomposition scales are supported (controlled by the \code{numScales} parameter).

%% ============================================================================
    \section{Command Module Reference}
    \label{sec:commands}
%% ============================================================================

    The backend exposes \textbf{41 Tauri commands} across 9 modules, registered in \code{lib.rs} via \code{tauri::generate\_handler}. Of these, \textbf{20 are actively used} by the frontend UI and \textbf{21 are backend-ready} but awaiting UI integration.

    \begin{notebox}[Command Wiring Status]
        Commands marked with $\star$ are actively wired to UI components. Commands marked with $\circ$ have working backend implementations but no frontend panel yet.
    \end{notebox}

    \subsection{Image Module (\texttt{commands/image.rs})}

    \begin{table}[H]
        \centering
        \small
        \begin{tabularx}{\textwidth}{clXX}
    \toprule
    & \textbf{Command} & \textbf{Parameters} & \textbf{Returns} \\
    \midrule
    $\star$ & \cmd{process\_fits} & path, output\_dir & png\_path, dimensions, elapsed\_ms \\
    $\star$ & \cmd{process\_fits\_full} & path, output\_dir & png\_path, dims, header, histogram, stf \\
    $\circ$ & \cmd{process\_batch} & paths[], output\_dir & processed, failed, results[] \\
    $\circ$ & \cmd{get\_raw\_pixels\_binary} & path & ArrayBuffer (16B header + f32[]) \\
    $\star$ & \cmd{get\_raw\_pixels\_preview} & path, max\_dim & ArrayBuffer (downsampled, 16B header + f32[]) \\
    $\star$ & \cmd{export\_fits} & path, output\_path, stf opts, copy\_wcs? & output\_path, dims, file\_size \\
    $\star$ & \cmd{export\_fits\_rgb} & r/g/b\_path, output\_path, copy\_wcs? & output\_path, dimensions \\
    $\star$ & \cmd{resample\_fits\_cmd} & path, target\_w, target\_h, output\_dir & png\_path, fits\_path, dims \\
    \bottomrule
        \end{tabularx}
        \caption{Image module commands}
    \end{table}

    \subsection{Metadata Module (\texttt{commands/metadata.rs})}

    \begin{table}[H]
        \centering
        \small
        \begin{tabularx}{\textwidth}{clXX}
    \toprule
    & \textbf{Command} & \textbf{Parameters} & \textbf{Returns} \\
    \midrule
    $\star$ & \cmd{get\_header} & path & Map of 20 key FITS keywords \\
    $\star$ & \cmd{get\_full\_header} & path & All cards categorized, filter detection \\
    $\circ$ & \cmd{get\_fits\_extensions} & path & HDU list with types and dimensions \\
    $\circ$ & \cmd{get\_header\_by\_hdu} & path, hdu\_index & Header cards for specific HDU \\
    $\circ$ & \cmd{detect\_narrowband\_filters} & paths[] & Palette suggestion with channel mapping \\
    \bottomrule
        \end{tabularx}
        \caption{Metadata module commands}
    \end{table}

    \subsection{Analysis Module (\texttt{commands/analysis.rs})}

    \begin{table}[H]
        \centering
        \small
        \begin{tabularx}{\textwidth}{clXX}
    \toprule
    & \textbf{Command} & \textbf{Parameters} & \textbf{Returns} \\
    \midrule
    $\star$ & \cmd{compute\_histogram} & path & 65536 bins, stats (median/mean/$\sigma$/MAD), auto\_stf \\
    $\star$ & \cmd{compute\_fft\_spectrum} & path, output\_dir & width, height, pixels\_b64, dc/max magnitude, png\_path \\
    $\star$ & \cmd{detect\_stars} & path, sigma?, max\_stars? & stars[] (x,y,flux,fwhm,snr), background \\
    \bottomrule
        \end{tabularx}
        \caption{Analysis module commands}
    \end{table}

    \subsection{Visualization Module (\texttt{commands/visualization.rs})}

    \begin{table}[H]
        \centering
        \small
        \begin{tabularx}{\textwidth}{clXX}
    \toprule
    & \textbf{Command} & \textbf{Parameters} & \textbf{Returns} \\
    \midrule
    $\star$ & \cmd{apply\_stf\_render} & path, output\_dir, shadow, midtone, highlight & png\_path, dims, stf\_params \\
    $\circ$ & \cmd{generate\_tiles} & path, output\_dir, tile\_size? & tile\_size, levels[], original dims \\
    $\circ$ & \cmd{get\_tile} & path, output\_dir, level, col, row & tile\_path, cached flag \\
    \bottomrule
        \end{tabularx}
        \caption{Visualization module commands}
    \end{table}

    \subsection{Cube Module (\texttt{commands/cube.rs})}

    \begin{table}[H]
        \centering
        \small
        \begin{tabularx}{\textwidth}{clXX}
    \toprule
    & \textbf{Command} & \textbf{Parameters} & \textbf{Returns} \\
    \midrule
    $\circ$ & \cmd{process\_cube\_cmd} & path, output\_dir, frame\_step? & dims, collapsed paths, spectrum \\
    $\circ$ & \cmd{process\_cube\_lazy\_cmd} & path, output\_dir, frame\_step? & Same + total\_frames (streaming) \\
    $\star$ & \cmd{get\_cube\_info} & path & naxis1/2/3, bitpix, wavelengths \\
    $\circ$ & \cmd{get\_cube\_frame} & path, frame\_index, output\_path & frame\_index, output\_path, elapsed \\
    $\star$ & \cmd{get\_cube\_spectrum} & path, x, y & spectrum[], wavelengths[], elapsed \\
    \bottomrule
        \end{tabularx}
        \caption{Cube module commands}
    \end{table}

    \subsection{Astrometry Module (\texttt{commands/astrometry.rs})}

    \begin{table}[H]
        \centering
        \small
        \begin{tabularx}{\textwidth}{clXX}
    \toprule
    & \textbf{Command} & \textbf{Parameters} & \textbf{Returns} \\
    \midrule
    $\circ$ & \cmd{plate\_solve\_cmd} & path, sigma?, hints?, scale range? & ra/dec center, pixel\_scale, WCS matrix \\
    $\circ$ & \cmd{get\_wcs\_info} & path & center coords, pixel\_scale, FOV, corners \\
    $\circ$ & \cmd{pixel\_to\_world} & path, x, y & ra, dec, ra\_dec\_str \\
    $\circ$ & \cmd{world\_to\_pixel} & path, ra, dec & x, y \\
    \bottomrule
        \end{tabularx}
        \caption{Astrometry module commands}
    \end{table}

    \subsection{Stacking Module (\texttt{commands/stacking.rs})}

    \begin{table}[H]
        \centering
        \small
        \begin{tabularx}{\textwidth}{clXX}
    \toprule
    & \textbf{Command} & \textbf{Parameters} & \textbf{Returns} \\
    \midrule
    $\circ$ & \cmd{calibrate} & science, output\_dir, bias/dark/flat?, ratio? & png\_path, dims, applied flags \\
    $\circ$ & \cmd{stack} & paths[], output\_dir, $\sigma$ params, align? & png\_path, count, rejected, offsets \\
    $\star$ & \cmd{drizzle\_stack\_cmd} & paths[], output\_dir, scale, pixfrac, kernel & png, weight\_map, dims, offsets \\
    $\star$ & \cmd{drizzle\_rgb\_cmd} & r/g/b groups, output\_dir, drizzle params & png\_path, per-channel info \\
    $\star$ & \cmd{compose\_rgb\_cmd} & r/g/b\_path, output\_dir, stretch/wb/scnr & png\_path, per-channel STF, offsets \\
    $\circ$ & \cmd{run\_pipeline\_cmd} & input, output\_dir, frame\_step? & total, succeeded, failed, results \\
    \bottomrule
        \end{tabularx}
        \caption{Stacking module commands}
    \end{table}

    \subsection{Config Module (\texttt{commands/config.rs})}

    \begin{table}[H]
        \centering
        \small
        \begin{tabularx}{\textwidth}{clXX}
    \toprule
    & \textbf{Command} & \textbf{Parameters} & \textbf{Returns} \\
    \midrule
    $\circ$ & \cmd{get\_config} & (none) & has\_api\_key, urls, defaults, stretch params \\
    $\circ$ & \cmd{update\_config} & field, value & \{ updated: true \} \\
    $\circ$ & \cmd{save\_api\_key} & key, service? & \{ saved: true, service \} \\
    $\circ$ & \cmd{get\_api\_key} & (none) & is\_set, masked key \\
    \bottomrule
        \end{tabularx}
        \caption{Config module commands}
    \end{table}

    \subsection{Processing Module (\texttt{commands/processing.rs}) --- New in v0.3.0}

    \begin{table}[H]
        \centering
        \small
        \begin{tabularx}{\textwidth}{clXX}
    \toprule
    & \textbf{Command} & \textbf{Parameters} & \textbf{Returns} \\
    \midrule
    $\star$ & \cmd{deconvolve\_rl\_cmd} & path, output\_dir, iterations, psf\_sigma, psf\_size, regularization, deringing, dering\_threshold & png\_path, iterations\_run, convergence, elapsed \\
    $\star$ & \cmd{extract\_background\_cmd} & path, output\_dir, grid\_size, poly\_degree, sigma\_clip, iterations, mode & corrected\_png, model\_png, stats \\
    $\star$ & \cmd{wavelet\_denoise\_cmd} & path, output\_dir, num\_scales, thresholds[], linear & png\_path, scales\_applied, elapsed \\
    \bottomrule
        \end{tabularx}
        \caption{Processing module commands (v0.3.0)}
    \end{table}

%% ============================================================================
    \section{FITS I/O Implementation}
    \label{sec:fits_io}
%% ============================================================================

    \subsection{Memory-Mapped Extraction}

    FITS files are opened via \crate{memmap2}, avoiding loading entire files into memory. The extraction pipeline:

    \begin{enumerate}[nosep]
    \item Parse header sequentially in 2880-byte blocks until \code{END} keyword
    \item Compute data offset: $\text{offset} = \lceil \text{header\_bytes} / 2880 \rceil \times 2880$
    \item Memory-map the data region as a byte slice
    \item BITPIX-dependent byte-swapping from FITS big-endian to native \code{f32}
    \end{enumerate}

    For integer data (BITPIX $> 0$), the BSCALE/BZERO transform is applied:

    \begin{equation}
        \text{value}_{\text{physical}} = \text{BSCALE} \times \text{value}_{\text{stored}} + \text{BZERO}
        \label{eq:bscale}
    \end{equation}

    \subsection{Supported BITPIX Values}

    \begin{table}[H]
        \centering
        \begin{tabular}{clcl}
            \toprule
            \textbf{BITPIX} & \textbf{Type} & \textbf{Bytes/px} & \textbf{Conversion} \\
            \midrule
            8 & Unsigned 8-bit int & 1 & Direct cast + BSCALE/BZERO \\
            16 & Signed 16-bit int & 2 & Big-endian swap + BSCALE/BZERO \\
            32 & Signed 32-bit int & 4 & Big-endian swap + BSCALE/BZERO \\
            $-32$ & IEEE 754 float & 4 & Big-endian swap \\
            $-64$ & IEEE 754 double & 8 & Big-endian swap $\to$ \code{f32} \\
            \bottomrule
        \end{tabular}
        \caption{FITS BITPIX type handling}
    \end{table}

%% ============================================================================
    \section{ASDF I/O Implementation (v0.3.0)}
    \label{sec:asdf_io}
%% ============================================================================

    AstroBurst includes the first Rust implementation of the \textbf{Advanced Scientific Data Format} (ASDF) reader, targeting NASA's Roman Space Telescope data products.

    \subsection{Format Structure}

    An ASDF file consists of three sections:
    \begin{enumerate}[nosep]
    \item \textbf{YAML tree} --- Metadata, data model, and WCS information serialized as YAML
    \item \textbf{Binary blocks} --- N-dimensional array data with optional compression
    \item \textbf{Block index} --- Byte offsets for random access to blocks
    \end{enumerate}

    \subsection{Decompression Support}

    Binary blocks may be compressed with zlib (\crate{flate2}), bzip2 (\crate{bzip2}), or lz4 (\crate{lz4\_flex}). The reader auto-detects the compression codec from the block header and decompresses transparently.

    \subsection{Roman Data Model Traversal}

    Roman Space Telescope ASDF files use a nested data model. The reader traverses the YAML tree to locate the science data array at \code{roman.data} or \code{roman.meta.exposure.data}, extracts the associated \code{ndarray} block reference, and converts it to \code{Array2<f32>} via the \code{AsdfImage} bridge.

    \subsection{gWCS Extraction}

    The generalized World Coordinate System (gWCS) stored in \code{roman.meta.wcs} is parsed to extract celestial reference coordinates and pixel scale, enabling coordinate overlay and astrometric context for Roman data.

    \subsection{Auto-Dispatch}

    The \code{extract\_image\_resolved} and \code{load\_cached} functions auto-detect file format by extension (\code{.asdf} vs \code{.fits/.fit/.fts}) and dispatch to the appropriate reader. The frontend accepts both formats transparently via the same drag-and-drop and file picker interface.

%% ============================================================================
    \section{WebGPU Compute Pipeline}
    \label{sec:webgpu}
%% ============================================================================

    The STF stretch is implemented as a WebGPU compute shader (WGSL) for real-time rendering:

    \begin{lstlisting}[style=bashcode, title={\small STF Compute Shader (simplified WGSL)}]
@group(0) @binding(0) var<storage, read> input: array<f32>;
@group(0) @binding(1) var<storage, read_write> output: array<u32>;
@group(0) @binding(2) var<uniform> params: StfParams;

fn mtf(x: f32, m: f32) -> f32 {
    return (m - 1.0) * x / ((2.0 * m - 1.0) * x - m);
}

@compute @workgroup_size(256)
fn main(@builtin(global_invocation_id) id: vec3<u32>) {
    let idx = id.x;
    let v = (input[idx] - params.shadow) / (params.highlight - params.shadow);
    let stretched = mtf(clamp(v, 0.0, 1.0), params.midtone);
    let byte_val = u32(clamp(stretched * 255.0, 0.0, 255.0));
    output[idx] = (255u << 24u) | (byte_val << 16u) | (byte_val << 8u) | byte_val;
}
    \end{lstlisting}

    The shader processes pixels in parallel with workgroup size 256. Falls back to Canvas 2D \code{putImageData} when WebGPU is unavailable (Chromium $<$ 113).

%% ============================================================================
    \section{Performance Benchmarks}
    \label{sec:performance}
%% ============================================================================

    \begin{table}[H]
        \centering
        \begin{tabular}{llrl}
            \toprule
            \textbf{Operation} & \textbf{Input Size} & \textbf{Time} & \textbf{Notes} \\
            \midrule
            Single FITS processing & 4096$\times$4096 (64\,MB) & 120\,ms & 533\,MB/s throughput \\
            Batch (10 frames) & 10$\times$64\,MB & 450\,ms & 1.4\,GB/s (Rayon parallel) \\
            Histogram + auto-STF & 4096$\times$4096 & 35\,ms & SIMD-accelerated \\
            Star detection ($\sigma{=}5$) & 4096$\times$4096 & 80\,ms & $\sim$3000 stars \\
            Sigma-clip stack & 10$\times$64\,MB & 2.1\,s & 5 iterations \\
            Drizzle 2$\times$ & 10$\times$64\,MB & 4.8\,s & Output: 8192$\times$8192 \\
            FFT power spectrum & 4096$\times$4096 & 95\,ms & \crate{rustfft} \\
            Cube spectrum extraction & 500$^2$$\times$2000 & 12\,ms & Memory-mapped \\
            WebGPU STF render & 4096$\times$4096 & 8\,ms & GPU compute \\
            Open 2\,GB IFU cube & 2\,GB datacube & 300\,ms & \crate{memmap2} lazy \\
            Drizzle RGB 2$\times$ & 3$\times$10$\times$64\,MB & 6.8\,s & All channels \\
            RGB compose + align & 3 channels & 1.8\,s & With cross-correlation \\
            \bottomrule
        \end{tabular}
        \caption{Performance benchmarks (AMD Ryzen 9 7950X, 64\,GB DDR5, NVMe)}
        \label{tab:benchmarks}
    \end{table}

    Binary size: $\sim$15\,MB.

%% ============================================================================
    \section{Dependencies}
    \label{sec:deps}
%% ============================================================================

    \subsection{Rust Crates}

    \begin{table}[H]
        \centering
        \small
        \begin{tabularx}{\textwidth}{llX}
    \toprule
    \textbf{Crate} & \textbf{Version} & \textbf{Purpose} \\
    \midrule
    \crate{tauri} & 2.x & Application framework, IPC, window management \\
    \crate{ndarray} & 0.16 & N-dimensional arrays, Rayon parallel iterators \\
    \crate{rayon} & 1.10 & Data-parallel batch processing \\
    \crate{memmap2} & 0.9 & Memory-mapped file I/O for FITS \\
    \crate{rustfft} & 6.2 & FFT for deconvolution and power spectrum \\
    \crate{num-complex} & 0.4 & Complex number support for FFT \\
    \crate{image} & 0.25 & PNG encoding/decoding \\
    \crate{serde\_yaml} & 0.9 & ASDF YAML tree parsing \\
    \crate{flate2} & 1.0 & zlib decompression (ASDF blocks) \\
    \crate{bzip2} & 0.4 & bzip2 decompression (ASDF blocks) \\
    \crate{lz4\_flex} & 0.11 & lz4 decompression (ASDF blocks) \\
    \crate{reqwest} & 0.12 & HTTP client for astrometry.net (optional) \\
    \crate{zip} & 0.6 & ZIP archive extraction for compressed FITS \\
    \crate{serde} / \crate{serde\_json} & 1.x & Serialization for Tauri commands \\
    \crate{anyhow} / \crate{thiserror} & 1.0+ & Error handling with context and typed errors \\
    \crate{base64} & 0.22 & Binary-to-text encoding for JSON IPC \\
    \crate{regex} & 1.10 & Filter detection pattern matching \\
    \crate{lazy\_static} & 1.5 & Static initialization \\
    \crate{dirs} & 5.0 & OS-native directory resolution \\
    \crate{tempfile} & 3.8 & Temporary files for ZIP extraction \\
    \bottomrule
        \end{tabularx}
        \caption{Rust dependencies}
    \end{table}

    \subsection{Frontend}

    \begin{table}[H]
        \centering
        \small
        \begin{tabularx}{\textwidth}{lX}
    \toprule
    \textbf{Package} & \textbf{Purpose} \\
    \midrule
    react / react-dom & UI framework \\
    @tauri-apps/api + plugins & Tauri IPC, dialog, filesystem \\
    framer-motion & Animations and transitions \\
    lucide-react & Icon system \\
    jszip / file-saver & Client-side ZIP export \\
    tailwindcss v4 & Utility-first CSS \\
    vite & Build toolchain \\
    typescript & Type safety \\
    \bottomrule
        \end{tabularx}
        \caption{Frontend dependencies}
    \end{table}

%% ============================================================================
    \section{Security Considerations}
    \label{sec:security}
%% ============================================================================

    \begin{itemize}[nosep]
    \item API keys (astrometry.net) are stored in the OS-native app data directory, never transmitted to third parties beyond the configured API endpoint.
    \item All file system access is constrained by Tauri capabilities (\code{default.json}). Permissions are scoped to home, desktop, and appdata directories.
    \item No telemetry, analytics, or network calls are made except for explicit plate solving requests initiated by the user.
    \item FITS and ASDF files are processed locally; no data leaves the machine unless plate solving is triggered.
    \end{itemize}

%% ============================================================================
    \section{Known Limitations}
    \label{sec:limitations}
%% ============================================================================

    \begin{enumerate}[nosep]
    \item \textbf{21 unwired commands} --- Plate solving, calibration, sigma-clip stacking, tile deep zoom, WCS overlay, narrowband auto-detection, and config UI panels are backend-ready but lack frontend integration
    \item \textbf{Grayscale pipeline} --- Color FITS images require manual RGB channel assignment
    \item \textbf{Online plate solving only} --- Local index-based solving is planned
    \item \textbf{No undo/redo} --- Operations are destructive (original files preserved)
    \item \textbf{WebGPU requirement} --- Chromium 113+ needed; Canvas 2D fallback available
    \item \textbf{No session persistence} --- Reopening the app starts a fresh workspace
    \item \textbf{ASDF read-only} --- Writer not yet implemented; ASDF files can be loaded but not exported
    \item \textbf{No MAST API integration} --- JWST/Roman data must be downloaded manually
    \end{enumerate}

%% ============================================================================
    \section{Roadmap}
    \label{sec:roadmap}
%% ============================================================================

    \begin{table}[H]
        \centering
        \begin{tabular}{lll}
            \toprule
            \textbf{Feature} & \textbf{Priority} & \textbf{Status} \\
            \midrule
            Multi-extension FITS (MEF) & High & \textcolor{ForestGreen}{Done (v0.2)} \\
            Bicubic resampling & High & \textcolor{ForestGreen}{Done (v0.2)} \\
            Richardson-Lucy deconvolution & High & \textcolor{ForestGreen}{Done (v0.3)} \\
            Background extraction & High & \textcolor{ForestGreen}{Done (v0.3)} \\
            Wavelet noise reduction & High & \textcolor{ForestGreen}{Done (v0.3)} \\
            ASDF format support & High & \textcolor{ForestGreen}{Done (v0.3)} \\
            \midrule
            Wire 21 backend commands to UI & High & Planned (v0.4) \\
            Local plate solving & High & Planned \\
            Star removal & Medium & Planned (v0.5) \\
            Photometric calibration (Gaia DR3) & Medium & Planned (v0.5) \\
            PixelMath expressions & Medium & Planned (v0.6) \\
            Mosaic stitching & Medium & Planned (v0.6) \\
            Plugin architecture (WASM) & Medium & Design phase \\
            Undo/redo system & Medium & Planned \\
            MAST API integration & Low & Planned \\
            Live stacking mode & Low & Planned \\
            INDI/ASCOM integration & Low & Planned \\
            \bottomrule
        \end{tabular}
        \caption{Development roadmap}
    \end{table}

%% ============================================================================
    \appendix
    \section{Sample Test Data}
    \label{app:test_data}
%% ============================================================================

    The repository includes HST/WFPC2 narrowband FITS images in \code{tests/sample-data/}:

    \begin{table}[H]
        \centering
        \begin{tabular}{lllll}
            \toprule
            \textbf{File} & \textbf{Filter} & \textbf{$\lambda$} & \textbf{Hubble Palette} & \textbf{Description} \\
            \midrule
            \code{502nmos.fits} & {[OIII]} & 502\,nm & Blue channel & Oxygen III emission \\
            \code{656nmos.fits} & H$\alpha$ & 656\,nm & Green channel & Hydrogen alpha emission \\
            \code{673nmos.fits} & {[SII]} & 673\,nm & Red channel & Sulfur II emission \\
            \bottomrule
        \end{tabular}
        \caption{Sample FITS files --- Eagle Nebula (M16) region, 1600$\times$1600 float32}
    \end{table}

    All images: BITPIX $= -32$, WCS TAN projection, origin STScI-STSDAS. Public domain (NASA/ESA).

\end{document}
